---
title: "Using the package locally"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{local_use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installing and loading the package

```{r setup, results='hide', warning = FALSE, message = FALSE}
# Installing
install.packages("devtools")
devtools::install_github("BencePalfi/SampleSizeBF")

# Loading
library(SampleSizeBF)
```

# Calculate Bayes factors

You can calculate the Bayes factors with three different priors: normal, Cauchy, and uniform distributions.

## Normal prior

To calculate the Bayes factor with a normal distribution as a prior you can use the following code. TODO add more explanation.

```{r}
Bf_normal(sd = 1.5, obtained = 1, dfdata = 10000, mean_of_theory = 0, sd_of_theory = 0.5, tail = 1)
```

## Cauchy prior

To calculate the Bayes factor with a Cauchy distribution as a prior you can use the following code. TODO add more explanation.

```{r}
Bf_cauchy(sd = 1.5, obtained = 1, dfdata = 10000, mean_of_theory = 0, sd_of_theory = 0.5, tail = 1)
```

## Uniform prior

To calculate the Bayes factor with a uniform distribution as a prior you can use the following code. TODO add more explanation.

```{r}
Bf_uniform(sd = 1.5, obtained = 1, dfdata = 10000, lower = 0, upper = 0.5)
```

# Samplesize planning

You can plan your sample size TODO add more explanation

## Normal prior

TODO add more explanation

```{r}
Bf_samplesize_normal(sd_of_theory = 1.5, sd1 = 1.8, sd2 = NULL, tail = 1, threshold = 3, tpr = .8, n_start = 5, n_end = 100, step = 1)
```

## Cauchy prior

TODO add more explanation

```{r}
Bf_samplesize_cauchy(sd_of_theory = 1.5, sd1 = 1.8, sd2 = NULL, tail = 1, threshold = 3, tpr = .8, n_start = 5, n_end = 100, step = 1)
```

## Uniform prior

TODO add more explanation

```{r}
Bf_samplesize_uniform(upper = 1.5, sd1 = 1.8, sd2 = NULL, tail = 1, threshold = 3, tpr = .8, n_start = 5, n_end = 100, step = 1)
```


